---
title: "Human activity recognition with smartphone sensors"
author: "Alex Sosnovshchenko"
date: "September 24, 2014"
output: html_document
runtime: shiny
---

This is web-application demonstrates how our activity recognition algorithms works. 

```{r, echo=FALSE, warning=FALSE}
## Libraries loading
library('plyr')

library("caret")
library("rpart")
library("rpart.plot")

library("tree")
library("randomForest")
library("e1071")
```

```{r, echo=FALSE}
_read.motion.data <- function(path.to.file) {
  acc <- as.data.frame(scan(path.to.file, 
                            what=list(date='', sensorName='', 
                                      activityType='', motionDirection='', onBodyPosition='', 
                                      x=0, y=0, z=0, 
                                      accuracy=0, m_activityType=''), 
                            sep=',', comment.char="", multi.line=F, fileEncoding="UTF-8", 
                            na.strings="", flush=T, fill=T))
  acc$date = as.numeric(as.character(acc$date))
  acc$date = as.POSIXct(acc$date, origin="1970-01-01")
  colnames(acc)[1]<-"dates"
  return(acc)
}

_aggregateMotionData <- function(res) {
  sec <- cut(res$date, breaks='sec')
  res <- cbind(res, sec=sec)
  
  #counting magnitude
  res$magnitude = sqrt(as.numeric(res$x)^2+as.numeric(res$y)^2+as.numeric(res$z)^2)
  res <- res[res$sensorName != "Activity",]
  res <- res[res$sensorName != "Calibrated_Magnetic_Field",]

  #counting table of predictors
  res.summary <- ddply(res, ~sec+sensorName, summarise, 
                       activity.type=cat(
                         names(sort(summary(activityType), decreasing = T)[1])[1]," ",
                         names(sort(summary(motion.direction), decreasing = T)[1])[1]," ",
                         names(sort(summary(on.body.position), decreasing = T)[1])[1],
                         ),
                       mean=mean(magnitude), sd=sd(magnitude), 
                       max=max(magnitude), min=min(magnitude),
                       fft.max=max(abs(fft(magnitude)))
  )
  
  result <- NA
  for (level in levels(as.factor(res.summary$sensorName))) {
    lvl <- res.summary[res.summary$sensorName == level,]
    names(lvl)[4:8] <- paste(names(lvl)[4:8], "_", level, sep="")
    lvl <- cbind(lvl[,1],lvl[3:8])
    if (result == NA) {
      result <- lvl
    } else {
      result <- merge(x = result, y = lvl, by = "sec", all = TRUE)
    }
  }

  result$activity.type <- as.factor(result$activity.type)
  result <- result[complete.cases(result),]
  return(res.summary)
}

read.motion.data(path.to.folder) <- function() {
  filenames <- list.files(path.to.folder, pattern="*.csv", full.names=TRUE)
  res <- lapply(filenames, _read.motion.data)
  res <- Reduce(rbind, res)
  res.summary <- _aggregateMotionData(res)
  remove(filenames, res)
  return(res.summary)
}

train <- read.motion.data("valid_data/train")
test <- read.motion.data("valid_data/test")

```

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

